Using Personal Activity Diaries to Enhance Electronic Health Records

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
boo

% Existing approaches to electronic integrated health records have largely focused on centralised information architectures, where patient data is held in a single repository, and accessed over the internet.

%Many patients are wearing personal sensors that report high-frequency and high-resolution data about their lifestyle, which could benefit patients and clinicians when taken in clinical context.

We posit that significant gains in patient-clinician communications can be made by helping clinicians to better understand a patient's life between their visits to the doctor.  In this paper, we present an architecture for enabling electronic health records to be augmented with \emph{personal activity diaries}, high resolution records of a patient's daily life, derived automatically from personal activity sensors.  These activity diaries establish a shared context between the patient and clinician for discussing the patient's lifestyle and condition.

>>>>

% Existing approaches to electronic integrated health records have largely focused on centralised information architectures, where patient data is held in a single repository, and accessed over the internet. 
%Many patients are wearing personal sensors that report high-frequency and high-resolution data about their lifestyle, which could benefit patients and clinicians when taken in clinical context.

We posit that significant gains in patient-clinician communications can be made by helping clinicians to better understand a patient's life between their visits to the doctor. In this paper, we propose a mechanism for augmenting electronic health records with \emph{personal activity diaries}, high resolution records of a patient's daily life, derived automatically from personal activity sensors.  These activity diaries establish a shared context for discussing the patient's lifestyle and condition.
